Performance Optimization of Service Chain for vCPE in Small Networks with OpenFlow Switch

### 2017-03-16 netsoft_paper.tex
fix typo

\subsubsection{Stateful Processing Component (VNF Controller in VM/Container)}
This component is used to control the workflow, maintain the state associated with the VNF, and provide an interface for service providers or customers to configure and update the behavior of the stateless datapath processing component. We used an SDN controller to implement the VNF controller; and notably, we use southbound APIs of the SDN controller framework to manage the interface between the stateful and stateless components with the OpenFlow protocol, which was originally designed for this purpose.

@@

\section{Conlusion and Future Works}
The proposed vCPE framework enables deploying NFVs as edge of network and these VNFs are implemented with multiple flow table management model. In this way, the customers only need a SDN switch at local network, and some network functions that could not be realized by single table mechanism are also resolved. The experimental results show that the framework provides better performance in VNF compete over single table SDN application. The integration evaluation also demonstrates its flexibility to integrate with any other bonus application identification system, IDS or IPS

>>>>

\subsubsection{Stateful Processing Component (VNF Controller in VM or Container)}
This component is used to control the workflow, maintain the state associated with the VNF, and provide an interface for service providers or customers to configure and update the behavior of the stateless datapath processing component. We used an SDN controller to implement the VNF controller; and notably, we use southbound APIs of the SDN controller framework to manage the interface between the stateful and stateless components with the OpenFlow protocol, which was originally designed for this purpose.

@@

\section{Conclusion and Future Works}
The proposed vCPE framework enables deploying NFVs as edge of network and these VNFs are implemented with multiple flow table management model. In this way, the customers only need a SDN switch at local network, and some network functions that could not be realized by single table mechanism are also resolved. The experimental results show that the framework provides better performance in VNF compete over single table SDN application. The integration evaluation also demonstrates its flexibility to integrate with any other bonus application identification system, IDS or IPS
